Tool-driven Revolutions in Archaeological Science

### 2018-09-10 analysis/paper/jcaa-paper.Rmd
resorting Huvila_2018
maybe this is a better place?

We can see a compelling exploration of the concrete sense of a paradigm in the work of @Galison_1997, who has offered a tool-driven view of change in research communities. Galison analysed of the role of tools in twentieth century particle physics, starting with hand-crafted cloud chambers and bubble chambers and ending with digital counters of and computers. He identifies a profound change in physics when analog devices producing pictures were superseded by digital devices producing numerical data. At the heart of this change is a shift from an intuitive approach, stimulated by visual and pictorial model-building to an approach based on logic, calculation, and demonstration. The changes are not purely at the points of data collection and analysis, but extend to the social and economic organisation of science, with new categories of physicists emerging, people who are not quite experimenters and not quite theorists. (Add footnote: A similar question, if a bit more theoretical, has been raised by @Huvila_2018 for archaeologists, discussing what questions on archaeological practices and knowledge work should be answered to avoid a technologically determisitic approach to computational archaeology.) 
Dyson [-@Dyson_2000; -@dyson2012science] has further explored this tool-driven approach, linking the Galilean revolution to the use of the telescope in astronomy, and the Crick-Watson revolution to the use of X-ray diffraction.

@@

>>>>

We can see a compelling exploration of the concrete sense of a paradigm in the work of @Galison_1997, who has offered a tool-driven view of change in research communities. Galison analysed of the role of tools in twentieth century particle physics, starting with hand-crafted cloud chambers and bubble chambers and ending with digital counters of and computers. He identifies a profound change in physics when analog devices producing pictures were superseded by digital devices producing numerical data. At the heart of this change is a shift from an intuitive approach, stimulated by visual and pictorial model-building to an approach based on logic, calculation, and demonstration. The changes are not purely at the points of data collection and analysis, but extend to the social and economic organisation of science, with new categories of physicists emerging, people who are not quite experimenters and not quite theorists.  
Dyson [-@Dyson_2000; -@dyson2012science] has further explored this tool-driven approach, linking the Galilean revolution to the use of the telescope in astronomy, and the Crick-Watson revolution to the use of X-ray diffraction.

@@

As @Galison_1997 describes a shift in the practices of physicists, so does archaeological practice change in the digital age. What exactly this entails, is diverse and has been discussed more thoroughly by @Huvila_2018 who ventilate what questions on archaeological practices and knowledge work should be answered to avoid a technologically determisitic approach to computational archaeology.
